Aa Language Reference Manual

### 2017-04-17 v2/Ahir-asm/devel/docs/AaLRM.tex
LRM updated with  bitmap (permutation) stuff.

For example
\begin{verbatim}
( $bitmap ($bitcast ($uint<4>) _h3) 0 3 1 2 2 1 3 0 ) = _he
\end{verbatim}

Note: this expression is not currently supported in hardware,
but will eventually be, maybe.

>>>>

For example, 
\begin{verbatim}
// X has type $uint<4>
( $bitmap ($bitcast X) 0 3 1 2 2 1 3 0 ) = rX
\end{verbatim}
implements
\begin{verbatim}
rX[3] <- X[0], rX[1] <- X[2], 
   rX[2] <- X[1], rX[0] <- X[3]
\end{verbatim}
and
\begin{verbatim}
// X has type $uint<4>
( $bitmap ($bitcast X) 0 3 3 0) = rX
\end{verbatim}
implements (not that unmapped indices
are left undisturbed)
\begin{verbatim}
rX[3] <- X[0], rX[1] <- X[1], 
   rX[2] <- X[2], rX[3] <- X[0]
\end{verbatim}
